Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-12 doc/report/msc-report.tex
report: hypenation of swedish abstract.
report: added lists of figures and tables.
report: added front and first pages.
* chalmers-header.*: header image used on front page.
* msc-report.tex: content nad formatting of front and first pages.

\documentclass[a4paper,10pt]{report}
\usepackage{graphicx}
\usepackage{listings}

\author{Per Andersson, Fredrik M{\"o}llerstrand}
\title{Zohmg---a large scale data store for aggregated time-series-based
data. [DRAFT]}

\begin{document}
\maketitle

@@

Detta examensarbete beskriver ett datalager f{\"o}r multidimensionell
tidsseriebaserad data. M{\aa}tt {\"a}r summerade {\"o}ver multipla dimensioner.
Datalagret {\"a}r optimerat f{\"o}r dataextraheringshastighet: Ett av
designm{\aa}len {\"a}r att servera data i musklickshastighet f{\"o}r att
fr{\"a}mja utforskning av data i realtid.

@@

\pagebreak
\phantom{ }
\pagebreak

@@

\pagebreak
\phantom{ }
\pagebreak

\tableofcontents
\vfill
\pagebreak

@@

>>>>

\documentclass[a4paper,10pt]{report}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{chngpage}

\begin{document}

\newpage
\changepage{60mm}{}{}{-39mm}{}{-45mm}{}{}{}

\renewcommand\thepage{}

\begin{center}
    \includegraphics{chalmers-header.eps}
\end{center}

\vspace{60mm}

\begin{adjustwidth}[]{20mm}{-40mm}
    {\huge \textbf{Zohmg---a large scale data store for \\
    aggregated time-series-based data. [DRAFT]}}

    \vspace{6pt}

    \noindent {\large \textit{Master of Science Thesis}}

    \vspace{36pt}

    \noindent {\Large \textbf{PER ANDERSSON}}

    \noindent {\Large \textbf{FREDRIK M{\"O}LLERSTRAND}}

    \vfill

    \noindent Department of Computer Science and Engineering

    \noindent CHALMERS UNIVERSITY OF TECHNOLOGY

    \noindent G{\"o}teborg, Sweden, 2009
\end{adjustwidth}

\newpage
\renewcommand\thepage{\arabic{page}}
\changepage{-60mm}{}{}{39mm}{}{47mm}{}{}{}

\setcounter{page}{1}

\noindent The Author grants to Chalmers University of Technology and University
of Gothenburg the non-exclusive right to publish the Work electronically and in
a non-commercial purpose make it accessible on the Internet.

\noindent The Author warrants that he/she is the author to the Work, and
warrants that the Work does not contain text, pictures or other material that
violates copyright law.

\noindent The Author shall, when transferring the rights of the Work to a third
party (for example a publisher or a company), acknowledge the third party about
this agreement. If the Author has signed a copyright agreement with a third
party regarding the Work, the Author warrants hereby that he/she has obtained
any necessary permission from this third party to let Chalmers University of
Technology and University of Gothenburg store the Work electronically and make
it accessible on the Internet.

\vspace{64pt}

\noindent Zohmg---a large scale data store for aggregated time-series-based
data.

\noindent PER ANDERSSON

\noindent FREDRIK M{\"O}LLERSTRAND

\noindent {\copyright} PER ANDERSSON, August 2009

\noindent {\copyright} FREDRIK M{\"O}LLERSTRAND, August 2009

\noindent Examiner: DAVID SANDS

\vspace{72pt}

\noindent Department of Computer Science and Engineering

\noindent Chalmers University of Technology

\noindent SE-412 96 Göteborg

\noindent Sweden

\noindent Telephone + 46 (0)31-772 1000

\vfill

\noindent Department of Computer Science and Engineering

\noindent G{\"o}teborg, Sweden, 2009

@@

Detta examensarbete beskriver ett datalager f{\"o}r multidimensionell
tidsserie-baserad data. M{\aa}tt {\"a}r summerade {\"o}ver multipla dimensioner.
Datalagret {\"a}r optimerat f{\"o}r dataextraheringshastighet: Ett av
designm{\aa}len {\"a}r att servera data i musklickshastighet f{\"o}r att
fr{\"a}mja utforskning av data i realtid.

@@

\pagebreak
This page is intentionally left blank.
\pagebreak

@@

\pagebreak
This page is intentionally left blank.
\pagebreak

\tableofcontents
\vfill

\begin{minipage}{116mm}
    \listoffigures
\end{minipage}

\begin{minipage}{116mm}
    \listoftables
\end{minipage}

@@

\pagebreak
This page is intentionally left blank.
\pagebreak
